---
title: "MA615Assignment1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

# call built-in data mtcars.
data(mtcars)
```
Tidyverse is a coherent packet operating system for data manipulation, 
exploration and visualization with a common design philosophy.

```{r}
# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]
mtcars_mpg2

# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]
mtcars_mpg2

#just a wrong try: class(mtcars$cyl)
#just a wrong try: x1<-as.factor(mtcars$cyl)
#just a wrong try: or x1<-as.factor(mtcars$cyl)
#just a wrong try: class(x1)
#just a wrong try: mtcars_mpg2<-data.frame(mtcars_mpg2)
#just a wrong try: x2<-data.frame(x1)
#just a wrong try: names(x2)<-c("factor")
#just a wrong try: x3<-cbind(mtcars_mpg2,xx) 
#cannot bind, because the number are not same.
#just a wrong try: x3

#wrong try again: mtcars_mpg2<-data.frame(mtcars_mpg2)
#wrong try again: xx<-as.factor(mtcars_mpg2$cyl)
#wrong try again: x1<-data.frame(xx)
#wrong try again: x2<-cbind(mtcars_mpg2,x1)
```
Select uses dataframe[dataframe$onedata < x, ]
Reduce uses dataframe[ ,c(residual)]

```{r}
# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)
```
"hand_functions.R" is a function and you need to run it so that you can operate.

Echo =TRUE means they will be included in the final rendered version.
It will specify any global settings to be applied to the R Markdown script.

Echo =FALSE also is a parameter that Knitr will recognize, 
means the code itself will not appear in the final document.

```{r}
# Now use the function from hand_functions.R
sp_out <- sum_special(mtcars_mpg2)
```
Run this code to use the function.

```{r}
#library(esquisse)

#answer: adjustment of the data
cyl_adjust<-as.factor(mtcars_mpg2$cyl)
mtcars_mpg2<-cbind(mtcars_mpg2,cyl_adjust)

#esquisser(data = mtcars_mpg2, viewer = "browser")
```
When you need to use Esquisse, input "library(esquisse)" 
and "esquisser(data = mtcars_mpg2, viewer = "browser")".
If you don't use it, just add "#" before it,
otherwise it will run and get stuck.

```{r}
ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()
```
These operations are manually adjusted in Esquisse.

"geom_point" represents point plot.

"geom_smooth" represents a smoothing line in order to see what the trends look like.

"theme_minimal()" is a minimalistic theme with no background annotations.

```{r}
# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?

#answer: create cyl_adjust<-as.factor(cyl), then add cyl_adjust to mtcars_mpg2
ggplot(mtcars_mpg2, aes(x=as.factor(cyl), y=mpg)) + 
  geom_boxplot(fill="slateblue", alpha=0.2) + 
  xlab("cyl")

#use adjustment in RStudio or Esquisse:
#ggplot(mtcars_mpg2, aes(x=cyl_adjust, y=mpg)) 
#+ geom_boxplot(fill="slateblue", alpha=0.2) + xlab("cyl")
```
"geom_boxplot" represents box plot.

In my opinion, Esquisse can't draw this boxplot because there is no as.factor(cyl)
in Esquisse. In order to solve this issue, I create a cyl_adjust in mtcars_mpg2
so that Esquisse appears cyl_adjust which means as.factor(cyl) now. 
Put cyl_adjust in x and mpg in y, then choose boxplot mode, the issue works out.

